\documentclass{article}
\usepackage[margin=1in]{geometry}

\begin{document}

\title{Treespotters Daily Log}
\author{Christophe Rouleau-Desrochers}
\maketitle

The following is everything related to treespotters fieldwork. All daily log prior to this is in Fuelinex's daily log, available on its github in the notes folder.

\section*{18 April 2025}
Mao and I (Christophe) left Vancouver at 9pm tonight and headed to Boston. 

\section*{19 April 2025}
Arrive in Boston in the morning, Lizzie picked us up and we drove to weldhill and at dana greenhouse. We went to dana greenhouse, dropped off my stuff and went to explore the arboretum and cored 5 trees. We met Lizzie at Weld building around 4pm and went to do groceries. We went back to walter street, made dinner and went to bed.

\section*{ 20 April 2025}
Woke up at 8am, went to Walter street, had breakfast with Mao and cored trees at Peter's hills. Cored 8 trees and went to meet Lizzie and had lunch. We went to meet the treespotters! It was great talking to them. I showed them the cookies and the figure I printed to explain. Then we went to core a basswood and a white oak. Took a group picture and chatted for a little while before going our separate ways. Mao and I went to the maple area of the park and finished all the trees around there. Finished at 5pm.

\section*{21 April 2025}
Started around 10am this morning. We started with some hickories and then did all the oaks. Finished the day with the birches near Dana greenhouse. 

\section*{Day 5: 22 April 2025}
Slow morning (again) because we only have 5 trees left to core which are pretty close to Dana Greenhouse. Five shagbark hickories which were actually pretty good overall, except one core that had some rot in the middle of it. Finished before noon. I grabbed research gear and brought it back to Weld Hill. Worked from there all afternoon. I sent an draft email to Lizzie to wrap up the field work, wrote on every straw in case the tags get mixed up, filled the field sheets and transcribed it in an excel spreadsheet to make it easier to read. Then I selected photos for Victor for a paper he's publishing in PNAS. Cores were tucked in the lab to let them dry until we pick them up during summer. 

\section*{Day 6: 23 April 2025}
Worked on notes this morning and emailed Neil to get ice cream sometime.

\section*{Day 7: 24 April 2025}


\end{document}
